Testing gene methylation enrichment analysis approaches using simulated data

### 2023-10-23 figs/GSE158422_simulate.Rmd
geometric sim

>>>>

### parametric competitive with "top" aggregation

lactopres <- lapply(1:nrow(params) , function(j) {
  groupsize = params[j,1]
  delta = params[j,2]
  res <- mclapply(1:sims,function(i) {
    simlactop(genesetdatabase=gsets, myann=myann, mval=normal_mval, seed=i*100, frac_genes=0.5, frac_probes=0.5,
      groupsize=groupsize, delta=delta, num_dm_sets=num_dm_sets)
  },mc.cores=2)
  res <- do.call(rbind,res)
  return(res)
})

lactopres2 <- do.call(rbind,lapply(lactopres,colMeans))

lactopres2 %>% kbl(caption="LA parametric results (top agg)") %>% kable_paper("hover", full_width = F)

lactopres3p <- do.call(rbind,lapply(groupsizes, function (g) { lactopres2[params$groupsizes==g,"PREC"] }))
colnames(lactopres3p) <- deltas
rownames(lactopres3p) <- groupsizes
lactopres3p %>% kbl(caption="LA parametric precision (top agg)") %>% kable_paper("hover", full_width = F)

lactopres3r <- do.call(rbind,lapply(groupsizes, function (g) { lactopres2[params$groupsizes==g,"REC"] }))
colnames(lactopres3r) <- deltas
rownames(lactopres3r) <- groupsizes
lactopres3r %>% kbl(caption="LA parametric recall (top agg)") %>% kable_paper("hover", full_width = F)

F1(lactopres3p,lactopres3r) %>% kbl(caption="LA parametric F1 (top agg)") %>% kable_paper("hover", full_width = F)

### parametric competitive aggregation with geometric mean

lacgeores <- lapply(1:nrow(params) , function(j) {
  groupsize = params[j,1]
  delta = params[j,2]
  res <- mclapply(1:sims,function(i) {
    simlacgeo(genesetdatabase=gsets, myann=myann, mval=normal_mval, seed=i*100, frac_genes=0.5, frac_probes=0.5,
      groupsize=groupsize, delta=delta, num_dm_sets=num_dm_sets)
  },mc.cores=2)
  res <- do.call(rbind,res)
  return(res)
})

lacgeores2 <- do.call(rbind,lapply(lacgeores,colMeans))

lacgeores2 %>% kbl(caption="LA parametric results with geometric mean") %>% kable_paper("hover", full_width = F)

lacgeores3p <- do.call(rbind,lapply(groupsizes, function (g) { lacgeores2[params$groupsizes==g,"PREC"] }))
colnames(lacgeores3p) <- deltas
rownames(lacgeores3p) <- groupsizes
lacgeores3p %>% kbl(caption="LA parametric precision with geometric mean") %>% kable_paper("hover", full_width = F)

lacgeores3r <- do.call(rbind,lapply(groupsizes, function (g) { lacgeores2[params$groupsizes==g,"REC"] }))
colnames(lacgeores3r) <- deltas
rownames(lacgeores3r) <- groupsizes
lacgeores3r %>% kbl(caption="LA parametric recall with geometric mean") %>% kable_paper("hover", full_width = F)

F1(lacgeores3p,lacgeores3r) %>% kbl(caption="LA parametric F1 with geometric mean") %>% kable_paper("hover", full_width = F)
